An Investigation of Confusing Code Patterns in JavaScript

### 2023-02-13 s01.tex
Fixed a couple of very minor inconsistencies.

\begin{table}[th!]
\caption{Hypotheses Testing (correctness). Asterisks ($^{*}$) indicate a statistically significant difference. Using Bonferroni correction, a p-value is considered statistically significant if it is lower than 0.0021.}
 \centering
 {\scriptsize 
 \begin{tabular}{lrr}
   \toprule
Atom candidate & McNemar test &      Odds Ratio \\
\midrule
Object Destructuring      &   \textbf{$<$ 0.0001*} & $\infty$ \\
Type Conversion           &   \textbf{$<$ 0.0001*} & 12.00 \\
Change of Literal Encoding   &   \textbf{$<$ 0.0001*} & 28.00 \\
Comma Operator            &   \textbf{$<$ 0.0001*} & 11.50 \\
Lack of Indentation No Braces     &   \textbf{$<$ 0.0001*} &  11.0 \\
Assignment As Value       &   \textbf{$<$ 0.0001*} &  9.30 \\
Pre-Increment              &  \textbf{0.0003*} &    16.00 \\
Omitted Curly Braces      &  \textbf{0.0009*} &  6.30 \\
Array Destructuring       &  0.0023 &     7.50 \\
Post-Increment              &  0.0225 &     5.50 \\
Array Spread              &  0.0490 &    3.30 \\
Object Spread             &  0.0636 &     2.80 \\
Property Access           &  0.0636 &     2.80 \\
Infix Operator Precedence &  0.1796 &     2.50 \\
Arrow Function            &  0.2891 &     3.00 \\
Arithmetic As Logic       &  0.3323 &  1.80 \\
Automated Semicolon Insertion  &  0.3915 &  1.40 \\
Logic As Control Flow     &  0.4421 &  1.50 \\
%Constant Variables        &  0.5000 &     0.0 \\
Implicit Predicate        &  0.6900 &  1.30 \\
Lack of Indentation With Braces   &  0.7266 &  1.70 \\
Conditional Operator      &  0.7905 &  1.30 \\
Dead Unreachable Repeated &  1.0000 &     1.50 \\
Repurposed Variables      &   1.0000 &     1.00 \\
\bottomrule
\end{tabular}
}
\label{tab:repeated:misunderstanding}
\end{table}

>>>>

\begin{table}[th!]
\caption{Hypotheses Testing (correctness). Asterisks ($^{*}$) indicate a statistically significant difference. Using Bonferroni correction, a p-value is considered statistically significant if it is lower than 0.0021.}
 \centering
 {\scriptsize 
 \begin{tabular}{lrr}
   \toprule
Atom candidate & McNemar test &      Odds Ratio \\
\midrule
Object Destructuring      &   \textbf{$<$ 0.0001*} & $\infty$ \\
Type Conversion           &   \textbf{$<$ 0.0001*} & 12.00 \\
Change of Literal Encoding   &   \textbf{$<$ 0.0001*} & 28.00 \\
Comma Operator            &   \textbf{$<$ 0.0001*} & 11.50 \\
Lack of Indentation No Braces     &   \textbf{$<$ 0.0001*} &  11.0 \\
Assignment As Value       &   \textbf{$<$ 0.0001*} &  9.30 \\
Pre-Increment              &  \textbf{0.0003*} &    16.00 \\
Omitted Curly Braces      &  \textbf{0.0009*} &  6.30 \\
Array Destructuring       &  0.0023 &     7.50 \\
Post-Increment              &  0.0225 &     5.50 \\
Array Spread              &  0.0490 &    3.30 \\
Object Spread             &  0.0636 &     2.80 \\
Property Access           &  0.0636 &     2.80 \\
Infix Operator Precedence &  0.1796 &     2.50 \\
Arrow Function            &  0.2891 &     3.00 \\
Arithmetic As Logic       &  0.3323 &  1.80 \\
Automatic Semicolon Insertion  &  0.3915 &  1.40 \\
Logic As Control Flow     &  0.4421 &  1.50 \\
%Constant Variables        &  0.5000 &     0.0 \\
Implicit Predicate        &  0.6900 &  1.30 \\
Lack of Indentation With Braces   &  0.7266 &  1.70 \\
Conditional Operator      &  0.7905 &  1.30 \\
Dead Unreachable Repeated &  1.0000 &     1.50 \\
Repurposed Variables      &   1.0000 &     1.00 \\
\bottomrule
\end{tabular}
}
\label{tab:repeated:misunderstanding}
\end{table}

### 2023-02-13 s02.tex
Fixed a couple of very minor inconsistencies.

\begin{table}[htbp]
\caption{Summary of the correctness analysis}
\label{tab:difference-correctness}
\centering{
  {\scriptsize
  \begin{scriptsize}
\begin{tabular}{lrrr} \toprule
  Atom & Obfuscated & Clean & $\Delta$(\%)  \\ \midrule
  Comma Operator                &  28 &  65 & +132   \\ 
  Automatic Semicolon Insertion &  32 &  68 & +112   \\ 
  Post-Increment                &  48 &  64 & +33    \\ 
  Omitted Curly Braces          &  47 &  58 &  +23   \\
  Assignment as Value           &  56 &  68 &  +21   \\ 
  Implicit Predicate            &  58 &  68 &  +17   \\ 
  Logic as Control Flow         &  41 &  48 &  +17   \\ 
  Conditional Operator              &  60 &  66 &  +10   \\ 
  Pre-Increment                 &  50 &  53 &  +6    \\ 
  Arithmetic as Logic           &  64 &  63 &  -2    \\ \bottomrule

>>>>

\begin{table}[htbp]
\caption{Summary of the correctness analysis}
\label{tab:difference-correctness}
\centering{
  {\scriptsize
  \begin{scriptsize}
\begin{tabular}{lrrr} \toprule
  Atom candidate& Obfuscated & Clean & $\Delta$(\%)  \\ \midrule
  Comma Operator                &  28 &  65 & +132   \\ 
  Automatic Semicolon Insertion &  32 &  68 & +112   \\ 
  Post-Increment                &  48 &  64 & +33    \\ 
  Omitted Curly Braces          &  47 &  58 &  +23   \\
  Assignment as Value           &  56 &  68 &  +21   \\ 
  Implicit Predicate            &  58 &  68 &  +17   \\ 
  Logic as Control Flow         &  41 &  48 &  +17   \\ 
  Conditional Operator              &  60 &  66 &  +10   \\ 
  Pre-Increment                 &  50 &  53 &  +6    \\ 
  Arithmetic as Logic           &  64 &  63 &  -2    \\ \bottomrule
